%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{mathptmx}
\usepackage{hyperref}
\name{Horia Alexandru Maior} % Your name
\address{School of Computer Science, University of Nottingham, NG8 1BB, UK} % Your address
\address{horia.maior@nottingham.ac.uk} % Your phone number and email
%\address{horia-alexandru.maior@nottingham.edu.cn} % Your phone number and email
%\address{Mob: +44 7468420350 } % Your phone number and email
\address{\url{http://www.nottingham.ac.uk/~psxhama}}
\begin{document}
	
	

	%----------------------------------------------------------------------------------------
	%	Publication SECTION
	%----------------------------------------------------------------------------------------
	\begin{rSection}{Publications}
		\begin{rSubsection}{ }{ }{ }{Peer reviewed Conference Papers, Journal Papers}
			
			\item \textbf{Maior, H.A.}, Wilson, M.L., Sharples, S. \emph{Workload Alerts - Using Physiological Measures of Mental Workload to Provide Feedback during Tasks}. (Under Review) ToCHI2017 Transactions on Computer-Human Interaction.
			
			\item Muralidharan, A., \textbf{Maior, H.A.}, and Rao, S. \emph{A self-governing and decentralized network of smart objects to share electrical power autonomously}. (Under Review): Springer Open Journal on Infrastructure Complexity.
			
			\item Lukanov K., \textbf{Maior, H. A.}, and Wilson, M. L. \emph{Using fNIRS in Usability Testing: Understanding the Effect of Web Form Layout on Mental Workload.} In: CHI'16 ACM SIGCHI Conference on Human Factors in Computer Systems, San Jose, California, May 2016.(Acceptance rate 20\%)
			
			\item \textbf{Maior, H. A.} Pike, M., Wilson, M. L., and Sharples, S. \emph{Examining the Reliability of Using fNIRS in Realistic HCI Settings for Spatial and Verbal Tasks.} In: CHI'15 ACM SIGCHI Conference on Human Factors in Computer Systems, Seoul, Korea, April 2015. (Acceptance rate 20\%)
			
			\item \textbf{Maior, H. A.} and Rao, S. (2014.) \emph{A Self-Governing, Decentralized, Extensible Internet of Things To Share Electrical Power Efficiently.} In IEEE CASE 2014 International Conference on Automation Science and Engineering, 18th August 2014. Taipei Taiwan.
			
			\item Pike, M., \textbf{Maior, H. A.}, Porcheron, M., Sharples, S. and Wilson, M. L. (2014). \emph{Measuring the effect of Think Aloud Protocols on Workload using fNIRS.} In: CHI'14 ACM SIGCHI Conference on Human Factors in Computer Systems, April-May 2014, Toronto. (Acceptance rate 20\%)
			
			\item \textbf{Maior, H. A.}, Pike, M., Wilson, M. L., and Sharples, S. \emph{Continuous detection of workload overload: An fNIRS approach.} In Contemporary Ergonomics and Human Factors 2014: Proceedings of the international conference on Ergonomics \& Human Factors 2014, Southampton, UK, April 2014.
		\end{rSubsection}
		
		\begin{rSubsection}{ }{ }{ }{Workshop papers, Abstract Papers, Magazine Articles}
			
			\item Wilson, M.L., Alsuraykh N., \textbf{Maior, H.A.},  \emph{Measuring mental workload in IIR user studies with fNIRS}. 2017.
			\item \textbf{Maior, H.A.}, Sharples, S., and Wilson, M.L. \emph{Subjective and Objective Methods to Continuously Monitor Workload}. Neuroergonomics 2016: The brain at work and in everyday life, Paris, France 2016.
			\item \textbf{Maior, H.A.}, and Stringer, P. (2015) \emph{The Values of Games for Health and Well Being}. Interdisciplinary Reflections on Games and Human Values - Workshop , The ACM SIGCHI Annual Symposium on Computer-Human Interaction in Play (CHI PLAY), London, 2015.
			\item \textbf{Maior, H.A.}, Wilson, M.L. and Sharples, S. (2015) \emph{fNIRS in Human Factors.} 2FNIRS Workshop, Toulouse, France April 2015.
			\item \textbf{Maior, H.A.}, Pike, M. \emph{Measuring Work Overload.} The Ergonomist Magazine, May 2014.
			\item \textbf{Maior, H.A.}, Pike, M., Wilson, M.L. and Sharples, S. (2013) \emph{Directly Evaluating the Cognitive Impact of Search User Interfaces: a Two-Pronged Approach with fNIRs.} EuroHCIR 2013 Workshop, Dublin, Ireland, August 2013
		\end{rSubsection}
		
	\end{rSection}
	%\vspace{-2 mm}
	\newpage
	%----------------------------------------------------------------------------------------
	%	Research interests  SECTION
	%----------------------------------------------------------------------------------------
	\begin{rSection}{Research Interests}
		\begin{rSubsection}{Brain and Physiological data use for Human Computer Interaction}{ }{ }{ }
			\vspace{-5 mm}
			My research lies in the intersection between Human-Computer Interaction (HCI), Brain-Computer Interface (BCI), and Human Factors. I am looking into the integration of non-invasive brain and physiological sensors, such as functional Near Infrared Spectroscopy (fNIRS), in the field of HCI. More specifically, I am interested in how we can use such devices to sense physiological responses to human cognition and mental workload, and use this continuous, quantitative measure, as an additional channel of information about the user during interaction.
			
\begin{itemize}
	\item I have previously \textbf{presented} at CHI 2016, NeuroErgonomics 2016, CHI 2015, CHIPLAY 2015, 2FNIRS 2015, CHI 2014, IEEE RAS 2014, EHF 2014.
%	\vspace{-2mm}
	\item Often involved in the Review process for multiple conferences and journals - I have been awarded the \textbf{Excellent Reviewer Award} at ACM-CHI 2017 - I have reviewed for UIST 2017, International Journal of Human-Computer Studies, CHI-PLAY 2017, ACM-CHI 2016 (\textbf{Senior Reviewer} for LBW), UIST 2016, ACM-CHI 2015, ACM-CHIPLAY 2014, IEEE CASE 2014, and IIiX 2014.
%	\vspace{-2mm}
	\item Always involved into organising Academic Conferences - I am the \textbf{Associate Chair} for Courses at the ACM-CHI 2018 where I have previously acted as a Student Volunteer in 2016 and 2017.
%	\vspace{-2mm}
	\item  Memberships - Association for Computing Machinery (ACM), Chartered Institute of Ergonomics and Human Factors.
\end{itemize}
			
		\end{rSubsection}
		
	\end{rSection}

\end{document}
